Refinements for open automata

### 2022-07-14 2021-Refinement/paper/refinementarticle.tex
proof sketch

\TODO{[LUDO] proof sketch}

\TODO{The subtlety here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}

>>>>

The bisimulation relation that we consider is the one that makes $A_1$ and $A_2$ bisimilar, complemented with identity of configurations for $A_3$.
The proof relies on the fact that, by construction, all transitions of the composed automaton $A_1\subst{A_3}{k}$ are specified by open transitions of $A_1$. For the transitions that do not involve hole $k$, the transition of $A_1\subst{A_3}{k}$ is the same and simulation between $A_1$ and $A_2$ allows us to conclude directly. If the hole $k$ is involved the considered relation  implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because Post are deterministic.
